Circumpolar variations in Southern Ocean eddy dynamics:\\An ensemble approach

### 2021-05-21 paper/main.tex
editing paper

\correspondingauthor{Navid C. Constantinou}{navid.constantinou@anu.edu.au}

% \begin{keypoints}
% \item An isopycnal layered model, with a varying number of fluid layers, is used to assess relative importance of barotropic and baroclinic processes in the Southern Ocean.
% \item Both baroclinic and barotropic flows exhibit regimes in which mean zonal transport is insensitive to wind stress.
% \item Eddies actively shape the time-mean flow, irrespective of the instabilities from which they originate. 
% \end{keypoints}

\begin{abstract}
We study here this and that...

\noindent \textbf{Plain language summary} \\
\noindent In plain words, we do this and that...
\end{abstract}

@@

\section{Results}
Figure 1 - (a) TKE snapshot and (b) TKE climatology

@@

Figure 5 - Ri ration plot, and other global features

>>>>

\correspondingauthor{Andrew McC. Hogg}{Andy.Hogg@anu.edu.au}

\begin{keypoints}
\item Variations in the Southern Ocean eddy field are dominated by intrinsic, rather than forced, processes.
\item The forced component of the the variance is governed by the local wind stress input.
\item The eddy field lags variations in wind stress, with two clear timescales emerging: one at 6-9 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
\end{keypoints}

\begin{abstract}
Circulation in the Southern Ocean is unique in global ocean.
The strong wind stress forcing and buoyancy fluxes, in concert with the lack of continental boundaries, conspire to drive the Antarctic Circumpolar Current replete with an intense eddy field.
The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.
Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of the Southern Ocean eddy field.
We find that intrinsic processes dominate the eddy field.
Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescale -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
These results suggest that understanding Southern Ocean eddy dynamics requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.

\noindent \textbf{Plain language summary} \\
\noindent The Southern Ocean is the most turbulent region of the world's oceans.
The variations in this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
But it's hard to get information about these eddies, because they occur on small scales in a large ocean basin that is poorly observed.
In addition, the observational record is quite short, which makes it more difficult to use these observations to study what controls variation in the eddy field.
For this reason, we take an eddy-permitting ocean model, and run it 50 times with the same forcing (but a slightly different initial state).
The chaotic nature of the turbulent ocean means that these models runs diverge into different states.
We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external forcing that is common to all experiments (such as wind forcing).
We conclude that the Southern Ocean eddy field is dominated by intrinsic chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence. 
\end{abstract}

@@

\section{Results}
Figure 1 - (a) TKE snapshot and (b) TKE climatology and perhaps (c) ensemble spread in TKE.

@@

Figure 5 - Ri ratio plot, and other global features
